% Copyright © 2010 Jonathan Rascher.

% Use a basic, minimal resume class, and boost the font size a tiny bit.
\documentclass[12pt]{simplecv}

% TeX uses relatively large margins by default. This leads to very nice pages
% when the document being typeset consists on large blocks of flowing text. On a
% resume, however, it looks rather too sparse. We fix that by shrinking the
% margins a bit.
\usepackage[letterpaper,hmargin=0.9in,vcentering]{geometry}

% Set some nice fonts. You can download them here:
% * <http://www.fontsquirrel.com/fonts/District-Thin>
% * <http://www.fontsquirrel.com/fonts/PT-Sans>
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{District Thin}
\setsansfont[Mapping=tex-text]{PT Sans}

% Enable multiple column support.
\usepackage{multicol}

% Set up PDF extras.
\usepackage{hyperref}
\hypersetup{pdftitle={Jonathan Rascher's Resume},
            pdfauthor={Jonathan Rascher}}

% Widen the left topic column to accommodate long item labels.
\renewcommand{\topicmargin}{0.33\columnwidth}

\begin{document}
  % My contact information. I use custom commands instead of hardcoding these
  % details so that I can generate two versions of my resume: one with personal
  % included, and one with it omitted which is suitable for posting online.
  \leftheader{
    \contactemail \\
    \contactphone
  }

  \rightheader{
    \contactaddressone \\
    \contactaddresstwo
  }

  % Print the resume masthead.
  \title{\addfontfeature{LetterSpace=2.1}Jonathan Rascher}
  \maketitle

  % The primary content of my resume follows.
  \begin{topic}
    \item[Bachelor of Science] Computer Science -- North Central College.

    \item[Bachelor of Science] Mathematics -- North Central College.

    \item[Minor] Interactive Media Studies -- North Central College.

    \item Member of Alpha Lambda Delta freshman honor society.

    \item GPA: 4.0 on a 4.0 scale after 84.0 credit hours.

    \item Anticipated graduation date: June 2012.
  \end{topic}

  \section{Academic Awards \& Distinctions}
  \begin{topic}
    \item[Academic Year 2010] Recipient of Mary Anice Seybold Prize in Mathematics.

    Member of ACCA programming contest advanced team.

    Participant in Google FUSE summer undergraduate retreat.

    \item[Academic Year 2009] Recipient of Presidential Scholarship.

    Recipient of Science Scholarship.

    Recipient of Phi Theta Kappa Scholarship.

    Entrant in William Lowell Putnam Mathematical Competition.

    \item[Fall 2008--Spring 2010] Dean's List (North Central College).

    \item[Fall 2007--Fall 2008] Dean's List (Elgin Community College).

    \item Took first college courses as a high school sophomore through an early-admissions program at Elgin Community College.
  \end{topic}

  \newpage

  \section{Programming \& Markup Languages}
  \begin{multicols}{2}
    \begin{itemize}
      \item Adobe Flash
      \item Assembly\ (x86\ and\ Z-machine)
      \item Bourne shell
      \item C/C++
      \item C\#
      \item CSS
      \item F\#
      \item HTML/XHTML
      \item \LaTeX
      \item Java
      \item JavaScript
      \item PHP
      \item Python
      \item Visual Basic (classic \& .NET)
    \end{itemize}
  \end{multicols}

  \section{Relevant Concepts from Coursework \& Self-Learning}
  \begin{multicols}{2}
    \begin{itemize}
      \item Algorithms
      \item Computer graphics in OpenGL
      \item Computer system concepts
      \item Data structures
      \item Digital \& film photography
      \item Discrete mathematics \& proofs
      \item Linux administration
      \item Robotics on Parallax Javelin Stamp
      \item Single \& multivariate calculus
      \item Web programming
    \end{itemize}
  \end{multicols}

  \section{Work \& Volunteer Experience}
  \begin{topic}
    \item[Sept. 2004--present] Education volunteer -- Cosley Zoo.
    \item[June 2010--Sept. 2010] Co-op developer in DIS division -- Argonne National Laboratory.
    \item[March 2010--June 2010] Preceptor: Computer Animation with Flash -- North Central College.
    \item[Sept. 2009--March 2010] Web application developer -- North Central College.
    \item[Summer 2007, 2008] Food runner (2007), Cashier (2008) -- Kane Country Cougars.
    \item[Sept. 2003--Aug. 2007] Teen volunteer -- Bartlett Public Library.
  \end{topic}
\end{document}
