% Copyright © 2010 Jonathan Rascher.

% Use a basic, minimal resume class, and boost the font size a tiny bit.
\documentclass[11pt]{simplecv}

% TeX uses relatively large margins by default. This leads to very nice pages
% when the document being typeset consists on large blocks of flowing text. On a
% resume, however, it looks rather too sparse. We fix that by shrinking the
% margins a bit.
\usepackage[letterpaper,hmargin=0.88in,vcentering]{geometry}

% Set some nice fonts. You can download or purchase them here:
% * <http://friedrichalthausen.de/?page_id=411>
% * <http://www.josbuivenga.demon.nl/fertigo.html>
%
% XXX: XeTeX doesn't automatically find Vollkorn styles for some reason.
% XXX: Kerning in Vollkorn makes apostrophes look really bad, so we turn it off.
\usepackage{fontspec}
\setmainfont[BoldFont={*-Bold},
             ItalicFont={*-Italic},
             BoldItalicFont={*-BoldItalic},
             Kerning=Off,
             Ligatures=TeX]
            {Vollkorn}
\newfontfamily\fertigopro[Ligatures=TeX]{Fertigo Pro}

% Decrease (!) the default leading a tiny bit.
\renewcommand{\baselinestretch}{0.95}

% Tell the simplecv class about our cool new fonts.
\headerfont{\fertigopro}
\titlefont{\fertigopro\LARGE}
\sectionfont{\fertigopro}
\subsectionfont{\fertigopro}
\topiclabelfont{\fertigopro\itshape}
\topictitlefont{\fertigopro\itshape}

% Widen the left topic column to accommodate long item labels.
\renewcommand{\topicmargin}{0.345\columnwidth}

% Enable multiple column support.
\usepackage{multicol}

% Use xspace to automatically tweak spacing after macros.
\usepackage{xspace}

% Set up PDF extras.
\usepackage[dvipsnames,usenames]{color}
\usepackage[colorlinks,urlcolor=RawSienna]{hyperref}
\hypersetup{pdfpagemode=UseNone,
            pdftitle={Jonathan Rascher's Resume},
            pdfauthor={Jonathan Rascher},
            pdfstartview=FitH,
            pdfprintscaling=None}

% Give our ampersands a little love.
\newcommand{\amp}{\textit\&\xspace}

\begin{document}
  % My contact information.
  \leftheader{
    <\href{mailto:jon@bcat.name}{jon@bcat.name}> \\
    +1 630 917 2228
  }

  \rightheader{
    PO Box 135 \\
    Wayne, IL 60184-0135
  }

  % Print the resume masthead.
  \title{\addfontfeature{LetterSpace=3.0}Jonathan Rascher}
  \maketitle

  % The primary content of my resume follows.
  \begin{topic}
    \item[Bachelor of Science] Computer Science \amp Mathematics---North Central College.

    \item[Academic Minor] Interactive Media Studies---North Central College.

    \item Member of Alpha Lambda Delta freshman honor society.

    \item Grade-point average 4.0/4.0 after 96 credit hours.

    \item Anticipated graduation date: June 2012.
  \end{topic}

  \section{Academic Awards \amp Distinctions}
  \begin{topic}
    \item[Academic Yr.\ 2009--10] Entrant in William Lowell Putnam Mathematical Competition.

    Member of ACCA programming contest advanced team.

    \item[Academic Yr.\ 2010] Recipient of Mary Anice Seybold Prize in Mathematics.

    Participant in Google FUSE summer undergraduate retreat.

    \item[Academic Yr.\ 2009] Recipient of Presidential Scholarship.

    Recipient of Science Scholarship.

    Recipient of Phi Theta Kappa Scholarship.

    \item[Fall 2008--Fall 2010] Dean's List (North Central College).

    \item[Fall 2007--Fall 2008] Dean's List (Elgin Community College).

    \item Took first college courses as a high school sophomore through an early-admissions program at Elgin Community College.
  \end{topic}

  \newpage

  \section{Programming \amp Markup Languages}
  \begin{multicols}{2}
    \begin{itemize}
      \item Adobe Flash
      \item Assembly (x86 \amp Z-machine)
      \item Bourne shell
      \item C/C++
      \item C\#
      \item CSS
      \item F\#
      \item HTML/XHTML
      \item \LaTeX
      \item Java
      \item JavaScript
      \item PHP
      \item Python
      \item Visual Basic (.NET \amp classic)
    \end{itemize}
  \end{multicols}

  \section{Relevant Concepts from Coursework \amp Self-Learning}
  \begin{multicols}{2}
    \begin{itemize}
      \item Computer graphics in OpenGL
      \item Computer system concepts
      \item Data structures \amp algorithms
      \item Digital \amp film photography
      \item Discrete mathematics \amp proofs
      \item Linux administration
      \item Robotics on Parallax Javelin Stamp
      \item Single \amp multivariate calculus
      \item Undergraduate real analysis
      \item Web development
    \end{itemize}
  \end{multicols}

  \section{Work \amp Volunteer Experience}
  \begin{topic}
    \item[Jan. 2011--Present] Preceptor: Computer Science II---North Central College.
    \item[June 2010--Sept. 2010] Co-op developer in DIS division---Argonne National Laboratory.
    \item[March 2010--June 2010] Preceptor: Computer Animation with Flash---North Central College.
    \item[Sept. 2009--March 2010] Web application developer---North Central College.
    \item[Sept. 2004--March 2009] Education volunteer---Cosley Zoo.
    \item[Summer 2007, 2008] Food runner (2007), Cashier (2008)---Kane Country Cougars.
    \item[Sept. 2003--Aug. 2007] Teen volunteer---Bartlett Public Library.
  \end{topic}
\end{document}
